Universal Anonymous Signatures

### 2022-04-27 prism-backend/research/gsac/app-gsac.tex
Generic GSAC construction. Some reorganisation.

        \procedure{$\OPEN(\sig)$}{%
          \textrm{Let}~\cid~\textrm{be s.t.}~(\sig,\DAttrs,\msg) \in \SIG[\cid] \\
          \pcif \textrm{no such \cid exists, or there is more than one}: \\
          \pcind \pcreturn \bot \\
          \pcif \sig \in \CSIG: \pcreturn \bot \\
          (\upk,\Attrs,\oproof) \gets
          \Open(\gpk,\osk,\trans[\cid],\sig,\DAttrs,\msg) \\
%          \OSIG \gets \OSIG \cup \lbrace (\sig,\upk,\cred) \rbrace \\
%          \CCRED \gets \CCRED \cup \lbrace \cid \rbrace \\
          \pcreturn (\upk,\Attrs,\oproof) \\
        }

        \procedure{$\CHALb(\ccid_0,\ccid_1,\DAttrs,\msg)$}{%
          \pcif \ATTR[\ccid_0] \cap \ATTR[\ccid_1] \nsubseteq \DAttrs:
          \pcreturn \bot \\
          \pcif \cuid_0 \neq \bot \lor \cuid_1 \neq \bot: \pcreturn \bot \\
          \cuid_0 = \OWNR[\ccid_0];~\cuid_1 = \OWNR[\ccid_1] \\
          \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
 %         \pcif \ccid_0 \in \CCRED \lor \ccid_1 \in \CCRED: \pcreturn \bot \\
          \csig \gets \Sign(\gpk,\PRVUK[\cuid_b],\CRED[\ccid_b],
          \DAttrs,\msg) \\
          \CSIG \gets \CSIG \cup \lbrace \csig \rbrace \\
          \pcreturn \csig
        }

@@

>>>>

        \procedure{$\OPEN(\sig)$}{%
          \textrm{Let}~\cid~\textrm{be s.t.}~(\sig,\DAttrs,\msg) \in \SIG[\cid] \\
          \pcif \textrm{no such \cid exists, or there is more than one}: \\
          \pcind \pcreturn \bot \\
          \pcif \sig \in \CSIG: \pcreturn \bot \\
          (\upk,\oproof) \gets \Open(\gpk,\osk,\sig,\DAttrs,\msg) \\
%          \OSIG \gets \OSIG \cup \lbrace (\sig,\upk,\cred) \rbrace \\
%          \CCRED \gets \CCRED \cup \lbrace \cid \rbrace \\
          \pcreturn (\upk,\oproof) \\
        }

        \procedure{$\CHALb(\ccid_0,\ccid_1,\DAttrs,\msg)$}{%
          \pcif \DAttrs \nsubseteq \ATTR[\ccid_0] \cap \ATTR[\ccid_1]:
          \pcreturn \bot \\
          \pcif \cuid_0 \neq \bot \lor \cuid_1 \neq \bot: \pcreturn \bot \\
          \cuid_0 = \OWNR[\ccid_0];~\cuid_1 = \OWNR[\ccid_1] \\
          \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
 %         \pcif \ccid_0 \in \CCRED \lor \ccid_1 \in \CCRED: \pcreturn \bot \\
          \csig \gets \Sign(\gpk,\PRVUK[\cuid_b],\CRED[\ccid_b],
          \DAttrs,\msg) \\
          \CSIG \gets \CSIG \cup \lbrace \csig \rbrace \\
          \pcreturn \csig
        }

@@

\subsection{Concrete Instantiation with BBS+}
\label{sapp:gsac-instantiation}

Intuitively, the credentials that we generate for our \GSAC construction are
Pedersen commitments to $(\usk,\credid,\Attrs)$ tuples; i.e., they have
the following structure: $\gen{h}_0^r\gen{h}_1^{\usk}\prod_{i \in [2,\nattrs+1]}
\gen{h}_i^{\Attrs_i}$, where the exponent in $\gen{h_0}$ is a fresh random value
that ensures hiding, the exponent in $\gen{h_1}$ encodes the user private
key, and the remaining attributes are encoded in different
exponentiations. This will actually be part of a BBS+ signature, which makes it
easy to add subsequent and efficient zero-knowledge proofs. Concretely, we will
be using several \NIZK proof systems, one for the $\langle \Obtain,\Issue
\rangle$ interactive protocol, another for signing, and a third one for opening.
Each will have its own relation, that we define in the corresponding algorithm.
The concrete algorithms are as follows.

\paragraph{$\Setup(\secpar,\nattrs) \rightarrow \parm$.} %
Generates a bilinear group $\BB = (p,\GG_1,\GG_2,\GG_T,\gen{g}_1,\gen{g}_2,e) \gets
\PGen(\secpar)$, $\nattrs+4$ additional generators $\gen{g},\gen{h},\gen{h}_0,...,
\gen{h}_{\nattrs+1}$ of $\GG_1$. Returns $\parm \gets
(\secpar,\nattrs,\BB,\gen{g},\gen{h},\gen{h}_0,...,\gen{h}_{\nattrs+1})$.

\paragraph{$\IKeyGen(\parm) \rightarrow (\ipk,\isk)$.} %
Parses \parm as $(\secpar,\dots)$ and runs $\NIZKcrs \gets \NIZKSetup(\secpar)$.
Outputs $\isk \gets \ZZ^*_p$, and $\ipk \gets (\NIZKcrs,\gen{g}_2^{\isk})$.

\paragraph{$\OKeyGen(\parm) \rightarrow (\opk,\osk)$.} %
Outputs $\osk \gets \ZZ^*_p$, and $\opk \gets \gen{g}^{\osk}$. This is the
opener's ElGamal encryption key pair \needcite.

\paragraph{$\UKeyGen(\parm) \rightarrow (\upk,\usk)$.} %
Outputs $\usk \gets \ZZ^*_p$, and $\upk \gets \gen{h}_1^{\usk}$. \upk will
simply be used to compute Pedersen commitments \needcite to \usk. However,
it is useful to precompute it, and we treat it as a sort of ``public key''.

\paragraph{$\langle \Obtain(\gpk,\usk,\Attrs),\Issue(\gpk,\isk,\Attrs) \rangle
  \rightarrow \langle \cred/\bot,\utrans/\bot \rangle$.} %
This interactive protocol is essentially a BBS+ signing  process. The user
commits to its private key, proves knowledge of the corresponding private
key, and asks the issuer to sign the commitment, along with any other arbitraty
set of revealed attributes \Attrs. For proving knowledge of the private key, we
define relation $\NIZKRel_{\Issue} = \lbrace (r, \usk), \Ccom: \Ccom =
\gen{h}_0^r\gen{h}_1^{\usk}\rbrace$.

\begin{itemize}
\item \underline{User}: Fetch fresh randomness $r \getr \ZZ^*_p,
  \Ccom \gets \gen{h}_0^r\gen{h}_1^{\usk}$, and compute $\NIZKproof \gets
  \NIZKProve^{\NIZKRel_{\Issue}}(\NIZKcrs,(r,\usk),
  \Ccom)$. Send $(\Ccom,\NIZKproof)$ to Issuer.
\item \underline{Issuer}: Run $\NIZKVerify^{\NIZKRel_{\Issue}}(\NIZKcrs,\Ccom,
  \NIZKproof)$ and return $0$ if it fails. Else, compute
  $x,\tilde{s} \getr \ZZ^*_p, A \gets
  (\gen{g}_1\Ccom h_0^{\tilde{s}} \prod_{i \in \Attrs}
  \gen{h}_i^{\Attrs_i})^{1/(\isk+x)}$.
  Send $(A,x,\tilde{s})$ to User, and output $\utrans \gets
  (\Ccom,(A,x,\tilde{s}),\Attrs,\NIZKproof)$.
\item \underline{User}: If $A = 1_{\GG_1}$: return $0$. Else, compute
  $s \gets r + \tilde{s}$. If $e(A,\gen{g}_2)^xe(A,\ipk) \neq
  e(\gen{g}_1\Ccom\gen{h}_0^{\tilde{s}}\prod_{i \in \Attrs}\gen{h}_i^{\Attrs_i},
  \gen{g}_2)$: return $0$. Else, return
  $(A,x,s)$.
\end{itemize}

\paragraph{$\Sign(\gpk,\usk,\cred,\DAttrs,\msg) \rightarrow \sig$.} %
To create a signature, the user first randomizes its BBS+ credential \cred and
encrypts its public key \upk (note that $\upk=\gen{h}_1^{\usk}$ with the
opener's encryption key. Then, we extend the usual NIZK protocol for proving
knowledge of BBS+ signatures \cite{cdl16b} to, in addition to proving knowledge
of a signature (which, for us is the user credential), also prove that the
attribute encoding \usk within the credential match the encrypted value.
Finally, the user commits to \msg, and includes this commitment within the
proof. For this, we define relation
$\NIZKRel_{\Sign}= \lbrace (r,\usk,\Attrs,r_2,r_3,s',\msg),(\DAttrs,c_1,c_2,
\Cmsg): \Cmsg = \gen{h}^\msg \land c_1 = g^r \land c_2 = \opk^r\gen{h}_1^{\usk}
\land \hat{A}/d = (A')^{-x}\gen{h}_0^{r_2} \land
\gen{g}_1 \prod_{i \in \DAttrs} \gen{h}_i^{\Attrs_i} =
d^{r_3}\gen{h}_0^{-s'}\gen{h}_1^{-\usk}
\prod_{i \notin \DAttrs} \gen{h}_i^{-\Attrs_i} \rbrace$.

\begin{itemize}
\item Parse \gpk as $(\ipk,\opk)$, and \cred as $(A,x,s)$.
\item Re-randomize \cred as $r_1,r_2 \getr
  \ZZ^*_p, r_3 \gets r_1^{-1}, s' \gets s - r_2r_3$, $A' \gets A^{r_1},
  \hat{A} \gets (A')^{-x}(\gen{g}_1\gen{h}_0^s\gen{h}_1^{\usk}
  \prod_{i \in \Attrs}\gen{h}_i^{\Attrs_i})^{r_1}$,
  $d \gets (\gen{g}_1\gen{h}_0^s\gen{h}_1^{\usk}
  \prod_{i \in \Attrs}\gen{h}_i^{\Attrs_i})^{r_1}\gen{h}_0^{-r_2}$.
\item Encrypt $\upk=\gen{h}_1^{\usk}$ with ElGamal as $r \getr \ZZ^*_p,
  c \gets (c_1 = \gen{g}^r,c_2 = \opk^r\gen{h}_1^{\usk})$.
\item Compute $\Cmsg \gets \gen{h}^\msg$ and
  $\NIZKproof \gets \NIZKProve^{\NIZKRel_{\Sign}}(\NIZKcrs,
  (r,\usk,\Attrs,r_2,r_3,s',\msg), (\DAttrs,c_1,c_2,\Cmsg))$.
\item Return $\sig \gets (c=(c_1,c_2),(A',\hat{A},d),\NIZKproof)$.
\end{itemize}

\paragraph{$\Verify(\gpk,\sig,\DAttrs,\msg) \rightarrow 1/0$.} %
Parse \gpk as $(\ipk,\opk)$ and $\sig$ as $(c=(c_1,c_2),
(A',\hat{A},d), \NIZKproof)$. Check that $A' \neq 1_{\GG_1}$ and $e(A',\ipk) =
e(\hat{A},\gen{g}_2)$. Compute $\Cmsg \gets \gen{h}^\msg,$ and return
$\NIZKVerify^{\NIZKRel_{\Sign}}(\NIZKcrs,(\DAttrs,c_1,c_2,\Cmsg),
\NIZKproof)$.

\paragraph{$\Open(\gpk,\osk,\sig,\DAttrs,\msg)
  \rightarrow (\upk,\oproof)/\bot$.} %
For open algorithms, we define the following relation for correct decryption of
ElGamal ciphertexts: $\NIZKRel_{\Open} = \lbrace \osk,(c_1,c_2,\msg):
c_2/c_1^{\osk} = \msg \rbrace$. Given $\NIZKRel_{\Open}$, the opener first,
checks that $\Verify$ accepts the signature, and aborts otherwise. If \sig
is accepted, then parses \sig as $(c=(c_1,c_2),\cdot,\cdot)$.
Sets $\upk \gets c_2/c_1^{\osk}$. Finally, computes the proof of correct
decryption by running $\oproof \gets \NIZKProve^{\NIZKRel_{\Open}}(\NIZKcrs,
\osk,(\upk,c_1,c_2))$, and returns $(\upk,\oproof)$.

\paragraph{$\Judge(\gpk,\upk,\oproof,\sig,\DAttrs,\msg)
  \rightarrow 1/0$.} %
First, check that $\Verify$ accepts \sig, and abort otherwise. If the signature
is accepted, then parse \sig as $(c=(c_1,c_2),\cdot,\cdot)$ and return
$\NIZKVerify^{\NIZKRel_{\Open}}(\NIZKcrs,(c_1,c_2,\upk),\oproof)$.

% \commentwho{Jesus}{For consistency with \UAS, maybe remove the need to return
%   \Attrs in \Open, and return \DAttrs instead. Then, we do not need to pass
%   \trans as a parameter to \Open, as \DAttrs is already attested for in the
%   signature being opened. It also makes sense from the point of view that we
%   are already revealing \upk, which would allow tracing; but otherwise don't
%   reveal anything else about the attributes of \upk -- attributes that whoever
%   requested the signature (the verifier) didn't seem to consider necessary, as
%   s/he only requested \DAttrs. Still, if we make this modification, mention the
%   possibility to return \Attrs, and the option to do it via adding \trans as a
%   parameter to \Open (or including an encryption of all attributes in the
%   signature, which is probably unrealistic.)}

### 2022-04-27 prism-backend/research/gsac/construction-uas.tex
Added formalisation of commitment schemes.
Generic GSAC construction. Some reorganisation.

\section{\CUASGen: A Generic \UAS Construction}
\label{sec:gen-construction}

@@

\subsection{Building Blocks}
\label{ssec:bblocks}

\paragraph{Vector Commitment schemes.} %
Defined as a tuple $(\CSetup,\CCommit)$. Algorithm $\Cparm \gets
\CSetup(\Csecpar)$ produces the parameters for committing to values. $\Ccom
\gets \CCommit(\Cparm, \msgset; r)$ produces a commitment \Ccom over a set of
messages \msgset, from which we may omit randomness $r$. \todo{Informally define
  hiding and binding, leaving formal definitions to the appendix.}

\paragraph{Public-Key Encryption.} %
Defined as a tuple $(\ESetup,\EKeyGen,\EEnc,\EDec)$. Algorithm $\Eparm \gets
\ESetup(\Esecpar)$ produces public parameters for the other algorithms.
$(\Eek,\Edk) \gets \EKeyGen(\Eparm)$ generates the encryption-decryption key
pair, algorithm $\Ec \gets \EEnc(\Eek,\msg)$ encrypts message \msg with
encryption key \Eek, producing ciphertext \Ec, and $\msg/\bot \gets \EDec(\Edk,
\Ec)$ decrypts ciphertexts using decryption key \Edk. \todo{Informally define
  security properties we'll need.}

\paragraph{Digital Signatures.} %
Defined as a tuple $(\SSetup,\SKeyGen,\SSign,\SVerify)$. Algorithm $\Sparm \gets
\SSetup(\Ssecpar)$ produces public parameters for the other algorithms.
$(\Svk,\Ssk) \gets \SKeyGen(\Sparm)$ generates the verification-signing key
pair, algorithm $\Ssig \gets \SSign(\Ssk,\msg)$ signs message \msg with
signing key \Ssk, producing signature \Ssig, and $1/0 \gets \SVerify(\Svk,
\Ssig,\msg)$ checks whether \Ssig is a valid signature over \msg, under
verification key \Svk. \todo{Informally define security properties we'll need.}

\paragraph{Non-Interactive Zero-Knowledge.} %
We use non-interactive zero-knowledge proofs of knowledge (NIZK), in the CRS
model \needcite. Informally, a NIZK scheme over an NP relation \NIZKRel is
defined as a tuple $(\NIZKSetup^\NIZKRel,\NIZKProve^\NIZKRel,
\NIZKVerify^\NIZKRel)$. Algorithm $\NIZKcrs \gets \NIZKSetup^\NIZKRel
(\NIZKsecpar)$ produces the common reference string \NIZKcrs. $\NIZKproof/\bot
\gets \NIZKProve^\NIZKRel(\NIZKcrs,\NIZKw,\NIZKx)$ creates a NIZK proof of
knowledge of witness \NIZKw for \NIZKx such that $(\NIZKw,\NIZKx) \in \NIZKRel$.
$1/0 \gets \NIZKVerify^\NIZKRel(\NIZKcrs,\NIZKx,\NIZKproof)$ verifies the proof.
\todo{Informally define security properties we'll need.}

\paragraph{Signatures over Blocks of Committed Messages, with proofs.} %
We use signature schemes that allow signing messages, or commitments to messages,
in blocks, and are compatible with (efficient) proof systems over the produced
signature and signed (commitments to) messages. For this purpose, we define such
schemes as a tuple $(\SBCMSetup,\SBCMKeyGen,\SBCMSign,\SBCMVerify)$. Algorithm
$\SBCMparm \gets \SBCMSetup(\SBCMsecpar)$ produces the public parameters for the
scheme. $(\SBCMvk,\SBCMsk) \gets \SBCMKeyGen(\SBCMparm)$ produces a
verification-signing key
pair. Algorithm $\SBCMsig \gets \SBCMSign(\SBCMsk,\Ccom,\msgset)$ produces a
signature over a set of committed messages \Ccom and a set of messages
\msgset, where either \Ccom or \msgset may be empty. $1/0 \gets
\SBCMVerify(\SBCMvk,\SBCMsig,\overline{\msgset})$ verifies a signature \SBCMsig
over message set $\overline{\msgset}$, which must contain both the messages that
were signed as commitments as well as those signed in ``the clear''. In
addition, the produced signatures must be compatible with (efficient) NIZK
proofs of knowledge of a signature, and of (arbitrary) claims over the signed
(committed) messages.
\todo{Informally define security properties we'll need.}

\subsection{Generic Construction \CUASGen}
\label{ssec:generic-construction-uas}

@@

\begin{itemize}
\item \uline{User}: Commit to the user secret key with $\Ccom \gets
  \CCommit(\usk)$. Compute proof $\NIZKproof \gets
  \NIZKProve^{\NIZKRel_{\Issue}}(\NIZKcrs_{\Issue},(\usk,\scred,\attrs_{\scred}),
  (\Ccom,\attrs))$. Send $(\Ccom,\NIZKproof)$ to Issuer.
\item \uline{Issuer}: Verify \NIZKproof with $\NIZKVerify^{\NIZKRel_{\Issue}}
  (\NIZKcrs_{\Issue},\NIZKproof,(\Ccom,\attrs,\sipk))$, and abort if it fails. Then,
  compute the credential by running $\cred \gets \SBCMSign(\SBCMsk,\Ccom,
  \attrs)$. Send \cred to User. Output $\utrans \gets (\Ccom,\attrs,\sipk,
  \cred,\NIZKproof)$.
\item \uline{User}: Verify the credential with $\SBCMVerify(\SBCMvk,\cred,
  \attrs \cup \lbrace \usk \rbrace)$. Reject if verification fails.
  Otherwise, return \cred.
\end{itemize}

@@

\paragraph{$1/0 \gets \Verify(\opk,\sipk,\sig,\yeval,\msg,\feval)$.} %
The ``cryptographic'' side of the verification essentially consists on checking
the NIZK proof. That is, parse \sig as $(\NIZKproof,\Ec)$ and check whether
$\NIZKVerify(\NIZKcrs,\NIZKproof,(\msg,\feval,\yeval,\Ec,\sipk)) = 1$. In
addition, the verifier may further check whether \yeval meets its needs.

@@

>>>>

\subsection{\CUASGen: A Generic \UAS Construction}
\label{ssec:generic-construction-uas}

@@

@@

\begin{itemize}
\item \uline{User}: Commit to the user secret key with $\Ccom \gets
  \CCommit(\usk)$. Compute proof $\NIZKproof \gets
  \NIZKProve^{\NIZKRel_{\Issue}}(\NIZKcrs_{\Issue},(\usk,\scred,\attrs_{\scred}),
  (\Ccom,\attrs,\sipk_{\scred}))$. Send $(\Ccom,\NIZKproof)$ to Issuer.
\item \uline{Issuer}: Verify \NIZKproof with $\NIZKVerify^{\NIZKRel_{\Issue}}
  (\NIZKcrs_{\Issue},\NIZKproof,(\Ccom,\attrs,\sipk))$, and abort if it fails. Then,
  compute the credential by running $\cred \gets \SBCMSign(\SBCMsk,\Ccom,
  \attrs)$. Send \cred to User. Output $\utrans \gets (\Ccom,\attrs,\sipk,
  \cred,\NIZKproof)$.
\item \uline{User}: Verify the credential with $\SBCMVerify(\SBCMvk,\cred,
  \attrs \cup \lbrace \usk \rbrace)$. Reject if verification fails.
  Otherwise, return \cred.
\end{itemize}

@@

\paragraph{$1/0 \gets \Verify(\opk,\sipk,\sig,\yeval,\msg,\feval)$.} %
The ``cryptographic'' side of the verification essentially consists on checking
the NIZK proof. That is, parse \sig as $(\NIZKproof,\Ec)$ and check whether
$\NIZKVerify(\NIZKcrs,\NIZKproof,(\msg,\feval,\yeval,\Ec,\sipk,\opk)) = 1$. In
addition, the verifier may further check whether \yeval meets its needs.

@@

%\input{security-uas.tex}
